Irt plot extra

### 2022-03-10 manuscript.Rmd
List of instruments removed from main manuscript

```{r relscale, include=F, warning=F, message=F}
#This chunk holds code for Relevant scales table in the manuscript
relevant.scale.data <- readxl::read_excel("Table_raw/relevant_scales.xlsx")

@@

```{r reltab2, results='asis'}
relevant.scale.data %>% 
apa_table(landscape =T,caption ="List of instruments measuring related constucts to LEBA", format = "latex",escape = T, font_size = "footnotesize", align = c("p{3cm}", rep("p{3.6cm}", ncol(relevant.scale.data))))

>>>>

```{r relscale, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
#This chunk holds code for Relevant scales table in the manuscript
relevant.scale.data <- readxl::read_excel("Table_raw/relevant_scales.xlsx")

@@

```{r reltab2, eval=FALSE, include=FALSE, results='asis'}
relevant.scale.data %>% 
apa_table(landscape =T,caption ="List of instruments measuring related constucts to LEBA", format = "latex",escape = T, font_size = "footnotesize", align = c("p{3cm}", rep("p{3.6cm}", ncol(relevant.scale.data))))
